A Fully Abstract Game Semantics for Countable Nondeterminism

### 2018-01-31 cones/paper/cones.tex
Acknowledgements.

Instead, we need to look at the combinatorial structure of the strategies.  
We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.  
In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.  
We recover the following version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} which now applies to the interpretation of PCF in $\G_{inn}$:
\begin{lemma}
  Let $M=C[\wn]$ be a term of type $\com$.  
  Write $\sigma_M\from\oc\bN\to\bC$ for the denotation of the term $\lambda n.C[n]$.  
  \begin{itemize}
    \item $M\converges\skipp$ if and only if there exists $\s\in \sigma_M$ such that $\s\vert_{\bC}=qa$.  
    \item $M\mustconverge$ if and only if $\sigma_M$ is \emph{winning}.
  \end{itemize}
  \label{lem:pcf-soundness-lemma}
\end{lemma}

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS501100000690}{National Science
    Foundation}{http://dx.doi.org/10.13039/501100000690} under Grant
  No.~\grantnum{GS501100000690}{EP/K018868/1}. Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  EPSRC.
\end{acks}

>>>>

Instead, we need to look at the combinatorial structure of the strategies.  
We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.

We define a deterministic strategy $\sigma\from A \implies B$ to be \emph{winning} if it is divergence-free and if for every $O$-play $s\in T_\sigma$ there exists some $t\in T_\sigma$ such that $s\prefix t$ and $t$ ends with a move in $B$.

Then for any strategy $\sigma_M$, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not winning.

We recover the following version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} which now applies to the interpretation of PCF in $\G_{inn}$:
\begin{lemma}
  Let $C[-]$ be a context of deterministic PCF.
  Write $\sigma_C\from\oc\bN\to\bN$ for the denotation of the term $\lambda n.C[n]$.  
  \begin{itemize}
    \item $C[\wn]\converges n$ if and only if there exists $\s\in \sigma_C$ such that $\s\vert_{\bN}=qa$.  
    \item $C\mustconverge$ if and only if $\sigma_C$ is winning.
  \end{itemize}
  \label{lem:pcf-soundness-lemma}
\end{lemma}

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS501100000690}{EPSRC}
  {http://dx.doi.org/10.13039/501100000690} under Grant
  No.~\grantnum{GS501100000690}{EP/K018868/1}. Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  EPSRC.
  I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
\end{acks}
